### 2021-10-29 article.tex
Introduction

In their introductory example,~\citepauthor{weirich2011generative} show how type family reduction can lead to unsoundness in the absence of role annotations.
Their presentation also includes a hypothetical translation of their example to Standard ML, which translates directly to Scala as follows:
%
\begin{lstlisting}
trait AgeClass {
  type Age
  def addAge(a: Age, i: Int): Int
}
object AgeObject extends AgeClass {
  type Age = Int
  def addAge(a: Age, i: Int): Int = a + i
}
\end{lstlisting}
%
In this example, type \dotty{Age} is abstract in \dotty{AgeClass} and concrete in \dotty{AgeObject}.
In the pre-role Haskell equivalent of this example, the unsoundness comes when the above definitions are combined with a type family that discriminates \dotty{Age} and \dotty{Int}.
Such type family would reduce differently in \dotty{AgeClass}, where the types are different, and in \dotty{AgeObject}, where those two types are synonyms, which can easily be exploited to obtain a runtime error.

>>>>

In their introductory example,~\citeauthor{weirich2011generative} show how type family reduction can lead to unsoundness in the absence of role annotations.
Their presentation also includes a hypothetical translation of their example to Standard ML, which translates directly to Scala as follows:
%
\begin{lstlisting}
trait AgeClass {
  type Age
  def addAge(a: Age, i: Int): Int
}
object AgeObject extends AgeClass {
  type Age = Int
  def addAge(a: Age, i: Int): Int = a + i
}
\end{lstlisting}
%
In this example, type \dotty{Age} is abstract in \dotty{AgeClass} and concrete in \dotty{AgeObject}.
In the pre-role Haskell equivalent of this example, the unsoundness comes when the above definitions are combined with a type family that discriminates \dotty{Age} and \dotty{Int}.
Such type family would reduce differently in \dotty{AgeClass}, where the types are different, and in \dotty{AgeObject}, where those two types are synonyms, which can easily be exploited to obtain a runtime error.
